---
output:   
  md_document:
    pandoc_args: ["--wrap=preserve"]
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# utilsR

<!-- badges: start -->
<!-- badges: end -->

`utilsR` is a personal R-based useful utils in data analysis. Feel free to use it :)

## Installation

You can install the released version of utilsR the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thereallda/utilsR")
```

NOTE: Visualization of PCA (`PCAplot`) and `BetweenStatPlot` are now implemented in `enONE` package, which can be installed with: 

```{r,eval=FALSE}
devtools::install_github("thereallda/enONE")
```

## Example

```{r,warning=FALSE,message=FALSE}
library(utilsR)
```

### PCAplot

PCA plot from counts matrix 
> Function to visualize PCA plot (`PCAplot`) now can be found at `enONE` package

```{r,message=FALSE}
set.seed(123)
counts_mat <- matrix(rnbinom(30000, mu=100, size=1), ncol=10)
groups <- rep(c('A','B'), each=5)
labels <- paste(rep(c('A','B'), each=5), 1:5, sep = '.')
enONE::PCAplot(counts_mat, 
               color = groups, 
               shape = groups, 
               label = labels, 
               vst.norm = TRUE, 
               repel = TRUE)
```


### BetweenStatPlot

Box-violin plot comparing values between groups

> `BetweenStatPlot` now can be found at `enONE` package

```{r}
data("iris")
head(iris)
enONE::BetweenStatPlot(iris, x = 'Species', y = 'Sepal.Width', color = 'Species',
                       comparisons = list(c('setosa','versicolor'), c('versicolor','virginica')),
                add.p = 'p')
```

### gene2goterm

Convert gene id to GO term

```{r}
# Convert gene id to GO term
gene2goterm(c("ENSMUSG00000025981", "ENSMUSG00000057363"), organism = 'mmusculus')
```

### ggVolcano

Volcano plot from DESeq2 results. 

Use `lfc.col` and `p.col` to specify the colname names of log-fold-change and adjusted p-value, respectively. 

Use `label.genes` to pass a vector of gene names (or gene ids consistent with rownames of the provided DE table) for label at the plot. 

```{r,warning=FALSE,message=FALSE}
library(DESeq2)
dds <- makeExampleDESeqDataSet(n=5000, m=4, betaSD = 5)
dds <- DESeq(dds)
res <- results(dds, contrast=c("condition","B","A"))
res.tab <- as.data.frame(res)
head(res.tab)
ggVolcano(res.tab,   
          lfc.col = "log2FoldChange",
          p.col = "padj",
          up.lfc.cutoff = 1,
          down.lfc.cutoff = -1,
          p.cutoff = 0.05,
          title = 'Condition: B/A',
          label.genes = c('gene877','gene763','gene4239','gene3325'),
          repel = T)
```
